---
title: "Kiva Scraping Analysis"
author: "Jeffrey Naecker"
date: "5/16/2019"
output: pdf_document
---

```{r setup, include=F, echo = F, message = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, ccache = TRUE)
```

```{r more-setup}
#### PACKAGES ####
library(dplyr)
library(lubridate)
library(ggplot2)

##### CONSTANTS #####
theme_set(theme_minimal())

timeLower = "2019-09-16 12:00:00"
timeUpper = "2019-09-17 12:00:00"

timeFirstMatch = "2019-09-16 12:45:01"
timeLastMatch  = "2019-09-16 16:00:10"

```

```{r load-data}
load("data/clean-data.rda")
```

Number of unique loans in sample: `r length(unique(observations$id))`.

```{r loans-vs-time}
observations %>%
  group_by(time = floor_date(time, "minute")) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = time, y = count)) +
    geom_line()
```

```{r match-vs-days-remaining}
# Does likelihood of being matched change over fundraising period?
ggplot(observations, aes(x = as.factor(floor(daysRemaining)), y = as.numeric(isMatchable))) +
  stat_summary(fun.y = "mean", geom = "point") +
  labs(title = "Fraction of matched loans vs days of fundraising remaining.",
       x     = "Days remaining in fundraising",
       y     = "Fraction matched")
```

```{r match-vs-datetime, include=F}
# Does likelihood of being matched change over calendar time?
ggplot(observations, aes(x = floor_date(time, "minute"), y = as.numeric(isMatchable))) +
  stat_summary(fun.y = "mean", geom = "point") +
  theme_bw() +
  labs(title = "Fraction of matched loans vs calendar time.",
       x     = "Date",
       y     = "Fraction matched")
```


```{r percent-funded-vs-days-remaining}
# How does percent funded change over fundraising period?
ggplot(observations, aes(x = as.factor(floor(daysRemaining)), y = percentFunded)) +
  stat_summary(fun.y = "mean", geom = "point") +
  theme_bw() + 
  labs(title = "Percent funded vs days of fundraising remaining.",
       x = "Days remaining in fundraising",
       y = "Percent funded")
```

```{r pilot-loans-fundraising}
pilot_loan_ids <- unique(pilot_results$`Loan ID`)


observations %>%
  mutate(id = as.character(id)) %>%
  filter(id %in% pilot_loan_ids) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  ggplot(aes(x = floor_date(time, "minute"), y = fundedAmount, color = isMatchable)) +
    geom_point() +
    facet_wrap(~id, ncol = 2) +
    theme_bw()
```

```{r pilot-loans-fundraising-detail}

observations %>%
  mutate(id = as.character(id)) %>%
  filter(id %in% pilot_loan_ids) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  ggplot() +
    geom_point(aes(x = floor_date(time, "minute"), y = fundedAmount, color = isMatchable)) +
##    geom_segment(aes(x = Purchase.Date + dhours(3), y = 0, xend = Purchase.Date + dhours(3), yend = You.Loaned), data = pilot_results, size = 1) +
    facet_wrap(~id, ncol = 2, scales = "free_y") +
    theme_bw()
```

Did loans meet our criteria?

```{r}
observations %>%
  filter(id %in% pilot_loan_ids) %>% 
  select(id, fundraisingDate, plannedExpirationDate, loanAmount) %>%
  unique() %>%
  arrange(fundraisingDate)
```


Of these loans, what transactions happened within the window where matching was active?
```{r, rows.print=20}

observations %>%
  filter(id %in% pilot_loan_ids) %>%
  mutate(id = as.character(id)) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  filter(loanAmount <= 1000) %>%
  filter(fundraisingDate < time & fundraisingDate >= time - dhours(24)) %>%
  group_by(id) %>%
  summarize(
    #loanAmount             = loanAmount[1],
    #plannedExpirationDate  = plannedExpirationDate[1],
    fundraisingDate        = fundraisingDate[1],
    totalObservations      = n(),
    percentMatched     = sum(isMatchable, na.rm = T)/totalObservations) %>%
  arrange(fundraisingDate) %>%
  print(tibble.width = Inf)
```



Other eligible loans (id ending in zero) that we didn't match. Were they matched by others during the window where matching was active?
```{r, rows.print=20}
observations %>%
  filter(id %% 10 == 0) %>%
  filter(! id %in% pilot_loan_ids) %>%
  mutate(id = as.character(id)) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  filter(loanAmount <= 1000) %>%
  filter(fundraisingDate < time & fundraisingDate >= time - dhours(24)) %>%
  group_by(id) %>%
  summarize(
    loanAmount             = loanAmount[1],
    fundraisingDate        = fundraisingDate[1],
    totalObservations      = n(),
    percentMatched     = sum(isMatchable, na.rm = T)/totalObservations) %>%
  arrange(fundraisingDate) %>%
  print(tibble.width = Inf)
```




Ineligible loans (id not ending in zero). Were they matched by others during the window where matching was active?

```{r, rows.print=20}
observations %>%
  filter(id %% 10 != 0) %>%
  mutate(id = as.character(id)) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  filter(loanAmount <= 1000) %>%
  filter(fundraisingDate < time & fundraisingDate >= time - dhours(24)) %>%
  group_by(id) %>%
  summarize(
    loanAmount             = loanAmount[1],
    fundraisingDate        = fundraisingDate[1],
    totalObservations      = n(),
    percentMatched     = sum(isMatchable, na.rm = T)/totalObservations) %>%
  arrange(fundraisingDate) %>%
  print(tibble.width = Inf)
```



Loans we could have matched (assuming correct criteria):

```{r, rows.print=20}
observations %>%
  filter(id %% 10 != 0) %>%
  mutate(id = as.character(id)) %>%
  filter(time >= ymd_hms(timeFirstMatch) & time <= ymd_hms(timeLastMatch)) %>%
  filter(loanAmount <= 1000) %>%
  filter(fundraisingDate < time & fundraisingDate >= time - dhours(24)) %>%
  select(id, fundraisingDate, plannedExpirationDate, loanAmount) %>%
  unique() %>%
  arrange(fundraisingDate)
```


